---
title: "Project 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries used
```{r}
library(dplyr)
library(ggcorrplot)
library(sjstats)
```

#Basic RSA (1-3)

# Read data and create Subjects
```{r}
# Read data and create 12 subject with added noise
NeuralResponses <- read.table('NeuralResponses')
set.seed(100)
for (i  in 1:12) {
  nam <- paste("subject", i, sep = "")
  assign(nam, rnorm(9200, 0, 1)+ NeuralResponses)
}

```


```{r}
# RDM function that returns a dataframe with RDMS
rdm <- function(df) {
  df<- df %>%
    t() %>%
    cor(method = 'pearson') %>% 
    as.data.frame() %>% 
    mutate_all(funs(1-.))
  colnames(df) <- c(1: ncol(df)) 
  return(df)
}

neur <- rdm(NeuralResponses)
neur %>% 
  ggcorrplot() + 
  ggtitle("RDM of og Neural Responses")
# RDM for the original NeuralResponses
NeuralResponses %>%
  t() %>%
  cor(method = 'pearson') %>% 
  as.data.frame() %>% 
  mutate_all(funs(1-.)) %>%
  ggcorrplot() + 
  ggtitle("RDM of Original Neural Responses")


# RDM for subjects
subject1 %>%
  t() %>%
  cor(method = 'pearson') %>%
  as.data.frame() %>%
  mutate_all(funs(1-.)) %>%
  ggcorrplot() + 
  ggtitle("RDM of Subject1")

subject2 %>%
  t() %>%
  cor(method = 'pearson') %>%
  as.data.frame() %>%
  mutate_all(funs(1-.)) %>%
  ggcorrplot() + 
  ggtitle("RDM of Subject2")

subject3 %>%
  t() %>%
  cor(method = 'pearson') %>%
  as.data.frame() %>%
  mutate_all(funs(1-.)) %>%
  ggcorrplot() + 
  ggtitle("RDM of Subject3")

subject4 %>%
  t() %>%
  cor(method = 'pearson') %>%
  as.data.frame() %>%
  mutate_all(funs(1-.)) %>%
  ggcorrplot() + 
  ggtitle("RDM of Subject4")

#### ----- ####

```
```{r}
meanMatrix = (subject1 + subject2 + subject3 + subject4 + subject5+ subject6+
                subject7 + subject8 + subject9 + subject10 + subject11 + subject12) / 12 
meanMatrix %>%
  t() %>%
  cor(method = 'pearson') %>%
  as.data.frame() %>%
  mutate_all(funs(1-.)) %>%
  ggcorrplot() + 
  ggtitle("averaged RDM of all subjects")

```

# Hypothesis Testing (4 - 10)
```{r}
# Binary Classification of of the images 
CategoryVectors <- read.table('CategoryVectors')

# Labels of the categories (12 categories)
CategoryLabels <- read.table('CategoryLabels')

# FOR CREATING THE MASK
# Function that loops through a vector 
# And compares each pair 
loopThruVec <- function(vector) {
  vec <- vector()
  for (x in 1:length(vector)) {
    for (y in 1:length(vector)) {
        if(vector[x] == vector[y]){
          vec <- append(vec, 0)
        }
        else{
          vec <- append(vec, 1)
        }
      }
  }
  return(vec)
}

# MATRIX SHOWING SAME ANIMACY (0) AND DIFFERENT ANIMACY (1)
animacyMask <- as.data.frame(matrix(loopThruVec(CategoryVectors$V1),
                nrow = length(CategoryVectors$V1),
                ncol = length(CategoryVectors$V1))) 
colnames(animacyMask) <- c(1:92) # Rename column names to the correct number for easier extraction later

# MATRIX SHOWING SAME Faceness (0) AND DIFFERENT Faceness (1)
faceMask <- as.data.frame(matrix(loopThruVec(CategoryVectors$V6),
                nrow = length(CategoryVectors$V6),
                ncol = length(CategoryVectors$V6))) 
colnames(faceMask) <- c(1:92) # Rename column names to the correct number for easier extraction later



# Give mask, dataframe over which mask is used, and value in mask
usemask <- function(mask, df, value) { 
 for (x in colnames(mask)) {
  for(y in row.names(mask)){
    if(mask[x,y] != value){ # If animacy is not the required animacy given
      df[x,y] = NA
      }
    }
 }
  return(df)  
}
# Function that removes self-correlations and double correlations
cleanMask <- function(df) {
  p <-1
  for (col in 1: ncol(df)) {
    for(row in p: nrow(df)){
      df[col,row] = NA
    }
    p <- p +1
  }
  for(col in 1:ncol(df)){
    for(row in 1:nrow(df)){
      if(col == row){
        df[col,row] = NA
      }
    }
  }
  return(df)
}
```

# Question 4 - Animacy of Original Data
```{r}
## Visualizations of different animacies for Original Neural Data
animacy0 <- usemask(animacyMask, rdm(NeuralResponses), 0) %>% 
  cleanMask()
animacy0 %>% 
  ggcorrplot() + 
  ggtitle("RDM of Responses with Same Animacy")

animacy1 <- usemask(animacyMask, rdm(NeuralResponses), 1) %>% 
  cleanMask()
animacy1 %>% 
  ggcorrplot() + 
  ggtitle("RDM of Responses with Different Animacy")

# Unpaired t-test
t.test(animacy0, animacy1)
```

# Question 5 - Animacy on subject and averaged subjects
```{r}
### T-Test Individual Subject (Subject1)
sub0 <- usemask(animacyMask, rdm(subject1), 0) %>% 
  cleanMask()

sub1 <- usemask(animacyMask, rdm(subject1), 1) %>% 
  cleanMask()
t.test(sub0, sub1) # T-Test for animacy in subject 1 

### T-Test Mean Subjects 
mmatrix0 <- usemask(animacyMask, rdm(meanMatrix),0) %>% 
  cleanMask()

mmatrix1 <- usemask(animacyMask, rdm(meanMatrix),1) %>% 
  cleanMask()
t.test(mmatrix0, mmatrix1)

#t.test(mmatrix1, mmatrix0)
```
# Question 6 - Faceness on Original Data
```{r}
# Testing Faceness 
face0 <- usemask(faceMask, rdm(NeuralResponses),0) %>% 
  cleanMask()

face1 <- usemask(faceMask, rdm(NeuralResponses),1) %>% 
  cleanMask()

t.test(face0, face1)
```

# Question 7 - Faceness of Animate Objects
```{r}
# Objects 1 - 48 are animate:  thus remove rows 49 onwards
animateNeural <- NeuralResponses[-c(49:92),] # Neural Responses with only Animate Objects 

# Create specific Face Mask for animated objects
anifaceMask <- faceMask <- as.data.frame(matrix(loopThruVec(CategoryVectors$V6[0:48]),
                nrow = length(CategoryVectors$V6[0:48]),
                ncol = length(CategoryVectors$V6[0:48]))) 
colnames(anifaceMask) <- c(1:ncol(anifaceMask)) 
anifaceMask %>% ggcorrplot()


aniface0 <- usemask(anifaceMask, rdm(animateNeural),0) %>% 
  cleanMask()
aniface0 %>% ggcorrplot()

aniface1 <- usemask(anifaceMask, rdm(animateNeural),1) %>% 
  cleanMask()
aniface1 %>% ggcorrplot()

# T-Test between animated objects with same and different face-ness
t.test(aniface0, aniface1)
```

# Question 8 - Humanity of objects
```{r}
# Objects 1 - 24 Human, 25-92 not human
# MATRIX SHOWING SAME Humanity (0) AND DIFFERENT Humanity (1)
humanMask <- as.data.frame(matrix(loopThruVec(CategoryVectors$V3),
                                  nrow = length(CategoryVectors$V3),
                                  ncol = length(CategoryVectors$V3)))
colnames(humanMask) <- c(1:92)
humanMask %>% ggcorrplot()


# normalMask <- function(vector) {
#   vec <- vector()
#   for (x in 1:length(vector)) {
#     for (y in 1:length(vector)) {
#         if(vector[x] == vector[y]){
#           vec <- append(vec, 0)
#         }
#         else{
#           vec <- append(vec, 1)
#         }
#       }
#   }
#   return(vec)
# }





humanMask <- as.data.frame(matrix())

# Compare Humanity (0) to other all other objects: 
human0 <- usemask(humanMask, rdm(NeuralResponses), 0) %>% 
  cleanMask()
human0 %>% 
  ggcorrplot() + 
  ggtitle("RDM of Responses with Same Humanity")

human1 <- usemask(humanMask, rdm(NeuralResponses), 1) %>% 
  cleanMask()
human1 %>% 
  ggcorrplot() + 
  ggtitle("RDM of Responses with Different Humaity")

# Unpaired t-test
t.test(human0, human1)


### Then -- select only animate objects


########## Animated Human Objects vs Animated NonHuman Objects #####
# Objects 1 - 48 are animate:  thus remove rows 49 onwards
animateNeural <- NeuralResponses[-c(49:92),] # Neural Responses with only Animate Objects 

# Create specific Human Mask for animated objects
aniHumanMask <- humanMask <- as.data.frame(matrix(loopThruVec(CategoryVectors$V3[0:48]),
                nrow = length(CategoryVectors$V3[0:48]),
                ncol = length(CategoryVectors$V3[0:48]))) 
colnames(aniHumanMask) <- c(1:ncol(aniHumanMask)) 
aniHumanMask %>% ggcorrplot()


anihuman0 <- usemask(aniHumanMask, rdm(animateNeural),0) %>% 
  cleanMask()
anihuman0 %>% ggcorrplot()

anihuman1 <- usemask(aniHumanMask, rdm(animateNeural),1) %>% 
  cleanMask()
anihuman1 %>% ggcorrplot()

# T-Test between animated human objects and animated non-human objects
t.test(anihuman0, anihuman1)
```

# Question 9 - ANOVA for Animacy and Faceness having the same effect
```{r}
## Visualizations of different animacies for Original Neural Data
animacy0 <- usemask(animacyMask, rdm(NeuralResponses), 0) %>% 
  cleanMask()
animacy0 %>% 
  ggcorrplot() + 
  ggtitle("RDM of Responses with Same Animacy")

animacy1 <- usemask(animacyMask, rdm(NeuralResponses), 1) %>% 
  cleanMask()
animacy1 %>% 
  ggcorrplot() + 
  ggtitle("RDM of Responses with Different Animacy")

# Objects 1 - 48 are animate:  thus remove rows 49 onwards
animateNeural <- NeuralResponses[-c(49:92),] # Neural Responses with only Animate Objects 

# Create specific Face Mask for animated objects
anifaceMask <- faceMask <- as.data.frame(matrix(loopThruVec(CategoryVectors$V6[0:48]),
                nrow = length(CategoryVectors$V6[0:48]),
                ncol = length(CategoryVectors$V6[0:48]))) 
colnames(anifaceMask) <- c(1:ncol(anifaceMask)) 
anifaceMask %>% ggcorrplot()


aniface0 <- usemask(anifaceMask, rdm(animateNeural),0) %>% 
  cleanMask()
aniface0 %>% ggcorrplot()


### HOW AM I SUPPOSED TO DO THIS?
#anova_test <- aov(neural_matrix ~ face_animated_matrix + animacy_matrix)
#summary(anova_test)
#etaSquared(anova_test, type = 2, anova = TRUE)

# Need: 
#View(neur)
#View(aniface0)
#View(animacy0)


# Create anova vectors  -- put all NAs to 0 

## Anova Aniface0
anova_aniface0 <- aniface0
anova_aniface0[is.na(anova_aniface0)] <- 0
View(anova_aniface0)
for (i in 1:44) {
 anova_aniface0 <- cbind(anova_aniface0, 0) 
}
colnames(anova_aniface0) <- c(1:92)
for (i in 1:44) {
 anova_aniface0 <- rbind(anova_aniface0, 0) 
}
row.names(anova_aniface0) <- c(1:92)
View(anova_aniface0)

## Anova Animacy0
anova_animacy0 <- animacy0
anova_animacy0[is.na(anova_animacy0)] <- 0
View(anova_animacy0)

## Anova OG Neural
anova_neur <- cleanMask(neur)
anova_neur[is.na(anova_neur)] <- 0
View(anova_neur)

#Create dataframe  with column #1 original column #2 aniface0 column3 animacy0

# Function that takes all the values of the columns and extends them in to a single vector
colToVec <- function(df) {
  vec <- vector()
  for (i in 1: ncol(df)) {
    vec<- append(vec, df[,i])
  }
  return(vec)
}



# Create all vectors
neurvec <- colToVec(anova_neur)
aniface0vec <- colToVec(anova_aniface0)
animacy0vec <- colToVec(anova_animacy0)

# Check equal length
length(neurvec)
length(aniface0vec)
length(animacy0vec)

save(neurvec, aniface0vec, animacy0vec, file = "data.RData")

# Put all vectors in a single dataframe
anovadf <- data.frame()
anovadf <- cbind(anovadf, neurvec)
anovadf <- cbind(anovadf, aniface0vec)
anovadf<- cbind(anovadf, animacy0vec)
anovadf <- as.data.frame(anovadf)
View(anovadf)

# Perform the Anova test on the created Dataframe
anova_test <- aov(anovadf$neurvec ~ anovadf$aniface0vec + anovadf$animacy0vec)
anova_test
summary(anova_test)

eta_sq(anova_test)
eta_sq(anova_test, partial = TRUE)
omega_sq(anova_test)
cohens_f(anova_test)


anova_test2 <- aov(anovadf$neurvec ~ anovadf$animacy0vec + anovadf$aniface0vec)
summary(anova_test2)




# Create a GLM model and then do the Anova
linearmodel <- glm(neurvec ~ aniface0vec + animacy0vec, data = anovadf)
anova(linearmodel)
summary(anova(linearmodel))





```

TESTING STUFF DISREGARD: 
```{r}
# ## Test correlation between two rows: 
# #cor = cor()
# # Transposed Neural Data for Correlation Calculation
# transposedNeuralData <- as.data.frame(t(NeuralResponses))
# colnames(transposedNeuralData) <- c(1:92)
# #1- cor(testSpons[1], testSpons[2], method = 'pearson')
# 
# # Extract the rows 
# 
# # Returns pairs of same animacy, does not use the pairs that compare to itself (e.g. pair <0,0> is not returned)
# 
# # Create cells <- c(), append(cells, c(waarden))
# # Maak matrix hiervan, weet het aantal rijen
# # Maak hier dataframe van (colnames: pairX, pairY, animacy, dissimilarity waarde)
# 
# selectSameAnimacy <- function(df, animacy) {
#   cells <- c()    # Instantiate cells 
#   rows <- 0       # To track the amount of rows needed  to split the cells over
#   for (x in 1:ncol(df)) {
#     for (y in 1:nrow(df)) {
#       if(df[x,y] == animacy & x != y){
#         rows <- rows + 1
#         dissimilarity = 1 - cor(transposedNeuralData[x], transposedNeuralData[y], method = 'pearson')
#         cells <- append(cells, c(x,y,animacy, dissimilarity))
#         # print(paste(x,y))
#       }
#     }
#   }
#   m <- matrix(cells, nrow = rows, byrow = TRUE) # Create a matrix from the cells 
#   df <- as.data.frame(m) # Create a dataframe from the matrix
#   colnames(df) <- c("x","y","animacystate","dissimilarity") # Add column names to the dataframe
#   return(df)
# }
# 
# 
# 
# a <- selectSameAnimacy(animacyMatrix, 0)
# b <- selectSameAnimacy(animacyMatrix,1)
# 
# animacyMatrix %>%
#   t() %>%
#   cor(method = 'pearson') %>%
#   as.data.frame() %>%
#   ggcorrplot() + 
#   ggtitle("averaged RDM of all subjects")
# 
# 
# 
# ## TEST the Animacy Matrix with a smaller vector ####
# testVector <- c(0,0,1,1)
# 
# testAnimacy <- as.data.frame(matrix(loopThruVec(testVector),
#                                     nrow = length(testVector),
#                                     ncol = length(testVector)))

```





# Question 11 test unfinished --> 
```{r}
NeuroRDM <- read.table('NeuroRDM')
colnames(NeuroRDM) <- c(1: ncol(NeuroRDM)) 
# NeuroRDM Is already an RDM!
NeuroRDM %>% ggcorrplot()



meanMatrix <- meanMatrix%>%
  t() %>%
  cor(method = 'pearson') %>%
  as.data.frame() %>%
  mutate_all(funs(1-.)) 
colnames(meanMatrix) <- c(1: ncol(meanMatrix)) 
  meanMatrix %>%ggcorrplot() +
  ggtitle("averaged RDM of all subjects")
  
### Then exclude self correlations and duplicate correlations: 
cleanNeuroRDM <- cleanMask(NeuroRDM)
cleanNeuroRDM %>% ggcorrplot()
View(cleanNeuroRDM)

cleanMeanMatrix <- cleanMask(meanMatrix)
cleanMeanMatrix %>% ggcorrplot()


cor.test(as.vector((cleanNeuroRDM)), as.vector((cleanMeanMatrix)))
# Reshape


cor.test(na.omit(cleanNeuroRDM), na.omit(cleanMeanMatrix), method = 'pearson')
####  Compare two RDMS


View(as.vector(cleanMeanMatrix))

```


