---
title: "Assignment3"
author: "Saif"
date: "1/15/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

# Sample Code from the assignment
```{r}
library(ggplot2)
# we will work with points 1 to 250 (cm)
scale.points <- c(1:250)
# we create a dataframe for plotting
example.height <- data.frame(x = scale.points)
# we use sapply, which is a vectorized function application; see help if
# you don't understand it
# we add y, which is just the probability density function described above
# (normal distribution)
example.height$y <- sapply(example.height$x, function(x) {
dnorm(x, mean = 180, sd = 10)
})
# this starts the plot creation
g1 <- ggplot(example.height, aes(x = x, y = y))
# we make the plot more pretty: we specify it should fill in area and add
# labels
g1 <- g1 + geom_area(fill = "green", alpha = 0.4) + xlab("height") + ylab("P") +
theme_gray(20)
g1
```

# Create Literal Listener Function
```{r}
literal.listener <- function(x, threshold, densityf, cumulativef) {
ifelse(x >= threshold, densityf(x)/(1 - cumulativef(threshold)), 0)
}
```

# Sample Code 
```{r}
threshold <- 170
example.height$updated <- sapply(example.height$x, function(x) {
literal.listener(x = x, threshold = threshold, densityf = function(x) {
dnorm(x, 180, 10)
}, cumulativef = function(x) {
pnorm(x, 180, 10)
})
})
# this starts the plot creation
g1 <- ggplot(example.height, aes(x = x, y = y))
g1 <- g1 + geom_area(fill = "green", alpha = 0.4)
# we add the result of updated belief
g1 <- g1 + geom_area(aes(y = updated), fill = "steelblue", alpha = 0.4)
g1 <- g1 + xlab("height") + ylab("P") + theme_gray(20)
g1
```

# Sample code Expected Success Function
```{r}
expected.success <- function(threshold, scale.points, densityf, cumulativef) {
ifelse(threshold > min(scale.points), sum(sapply(scale.points[scale.points <
threshold], function(x) {
densityf(x) * densityf(x)
})), 0) + sum(sapply(scale.points[scale.points >= threshold], function(x) {
densityf(x) * literal.listener(x, threshold, densityf, cumulativef)
}))
}
```


```{r}
# Utility Function
utility <- function(threshold, scale.points, coverage.parameter, densityf, cumulativef){
    return(expected.success(threshold = threshold, scale.points = scale.points, densityf = densityf,
                    cumulativef) + (coverage.parameter * sum(sapply(scale.points[scale.points>=threshold],               function(x) {densityf(x)}))))
}


# Probability Threshold Function
probability.threshold <- function(threshold, scale.points, lambda, coverage.parameter, densityf, cumulativef){
    
    som = 0
    for(i in scale.points){
        som = som + exp(lambda * utility(threshold = i, scale.points = scale.points,
                                         coverage.parameter = coverage.parameter, densityf = densityf,
                                         cumulativef = cumulativef)) 
    }
    result = exp(lambda * utility(threshold = threshold,
                                  scale.points = scale.points, coverage.parameter = coverage.parameter,
                                  densityf = densityf, cumulativef = cumulativef)) / som
    
    return(result)
    
}


# Use Adjective Function
use.adjective <- function(degree, scale.points, lambda, coverage.parameter, densityf, cumulativef) {

    value = sum(sapply(scale.points[scale.points<=degree],
                       function(x) {probability.threshold(threshold = x, scale.points = scale.points, 
                                                          lambda = lambda, coverage.parameter = coverage.parameter,
                                                          densityf = densityf, cumulativef = cumulativef)}))
    return(value)

}




```

```{r}
# Testing the Functions: 
# probability.threshold is a probability, so if you sum up all values it
# generates, the result should be 1
round(sum(sapply(1:10, function(x) {probability.threshold(x, 1:10, 50, 0, function(x) {dnorm(x, 5, 1)}, 
                                                          function(x) {pnorm(x, 5, 1)})}))) == 1

# for narrow normal distribution, prob. threshold should be max just one
# value above the average
which(sapply(1:10, function(x) {probability.threshold(x, 1:10, 50, 0, function(x) {
  dnorm(x, 5, 1)
  }, function(x) {
    pnorm(x, 5, 1)
    })
  }) == max(sapply(1:10, function(x) {
    probability.threshold(x, 1:10, 50, 0, function(x) {
      dnorm(x, 5, 1)
      }, function(x) {
        pnorm(x, 5, 1)
        })
    }))) == 6

# use.adjective should be very unlikely on values 5 and smaller and very
# likely afterwards
round(sapply(1:10, function(x) {
  use.adjective(x, 1:10, 50, 0, function(x) {
    dnorm(x, 5, 1)
    }, function(x) {
      pnorm(x, 5, 1)
      })
  })[5], 3) == 0.005


round(sapply(1:10, function(x) {
  use.adjective(x, 1:10, 50, 0, function(x) {
    dnorm(x, 5, 1)
    }, function(x) {
      pnorm(x, 5, 1)
      })
  })[6], 3) == 1

```
Given the distribution of height as described above (normal distribution, mean=180, st.d.=10), summarize the probability of using a threshold and how likely the speaker will use the adjective tall. For the
summary, report at least two things. First, show two graphs: (i) what the probability of using threshold
looks like on the scale 1 − 250cm; (ii) the graph of the function σ on the same scale. Second, you should
state which degree point has the highest probability of being used as a threshold, and on which degree point
it is most likely the speaker will use the adjective tall. If the two values differ or are the same, say in a few
words why you think this is so. For the task, use free parameters λ = 50 and c = 0.


```{r}
# Question 1a 
vec <- vector()
for (threshold in 1:250) {
  #print(threshold)
  y<- probability.threshold(threshold , 1:250, 50, 0, function(x) {
  dnorm(x, 180, 10)
  }, function(x) {
    pnorm(x, 180, 10)
    })
  vec <- append(vec, y)
}
df <- data.frame(x = c(1:250), y = vec)
df

g2 <- ggplot(df, aes(x = x, y = y))
g2 <- g2 + geom_area(fill = "green", alpha = 0.4)
g2 <- g2 + xlab("height") + ylab("P") + theme_gray(20)
g2
```

```{r}
# Question 1b
vec <- vector()
for (threshold in 1:250) {
  #print(threshold)
  y<-   use.adjective(threshold, 1:250, 50, 0, function(x) {
    dnorm(x, 180, 10)
    }, function(x) {
      pnorm(x, 180, 10)
      })
  vec <- append(vec, y)
}
df2 <- data.frame(x = c(1:250), y = vec)
df2S

g3 <- ggplot(df, aes(x = x, y = y))
g3 <- g3 + geom_area(fill = "green", alpha = 0.4)
g3 <- g3 + xlab("height") + ylab("P") + theme_gray(20)
g3
View(vec)
```

```{r}


scale.points <- c(1:250) 
mylist <- list()
for(i in scale.points){
    z <- use.adjective(degree = i, scale.points = scale.points, lambda = 50, coverage.parameter = 0, densityf=function(x) {dnorm(x, 180, 10)}, cumulativef=function(x) {pnorm(x, 180, 10)})
    mylist <- append(mylist, z)
}


```


# Question 2: 

```{r}
# Create IQ normal distribution
iqdist <- dnorm(seq(1,150), mean = 100, sd = 30 )
plot(iqdist)

```


